Paper without a name

### 2014-05-30 Article.tex
Changes..

In a second step, we show how we experimentally this conjecture for $n$ from 2 to 6, and
how we demonstrated that the number of comparisons is an upper bound of the
optimal number of boxes for $n$ from 7 to 13 by optimizing the checking
algorithm and by constructing a precise configuration.

>>>>

In a second step, we show how we experimentally checked this conjecture for $n$ from 2 to 6, and
how we demonstrated that the number of comparisons is an upper bound of the
optimal number of boxes for $n$ from 7 to 13 by optimizing the checking
algorithm and by constructing a precise configuration.
